Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-08 ms.tex
still discussing reddening residuals

\subsection{Rectifying Reddening Residuals}
In this section we describe our attempts to eliminate the systematic
problems in the two-component reddening residuals shown in the left column
of Figure \ref{fig:resid}. We employed two main strategies: (1) recompute
the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
the input maps and/or changing the particular two-component model adopted and
(2) making spatial cuts to isolate sky regions in which the 
residuals are especially pristine (or especially problematic).

The following is a list of dust model modifications we tested, but 
proved to have little impact on the shape of the reddening residuals versus
$E(B-V)_{SFD}$ and $T_2$:

@@

However, we did find that changing the zero level offsets of the input maps 
had a significant effect on the strength of the anticorrelation between
reddening residual and $T_2$. In particular, we experimented with perturbing 
the zero level offset of \PLANCK~857 GHz while correspondingly changing the 
zero levels of the remaining \PLANCK~maps based on the prescription of 
$\S$\ref{sec:relzero}. We also experimented with changing the zero level of SFD
\verb|i100|, independent of the other zero levels. Unfortunately, completely
flattening the reddening residual dependence on $T_2$ required unreasonably 
large zero level changes. For example, flattening the $T_2$ residual required
adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Furthermore, we note that 
even relatively large zero level modifications had virtually no effect in 
eliminating the `bend' versus $E(B-V)_{SFD}$. Thus, simply changing the
zero level offsets showed a bit of promise in rectifying the residual 
temperature dependence, but of itself was not a sufficient solution.

The ony solution we were able to identify that both removed the `bend' vs.
$E(B-V)_{SFD}$ and the temperature dependence of the residual was cutting 
out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
completely eliminated the bending behavior of the residual versus 
$E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
QQ)

% but required offsets too big

@@

% discuss changing global params and offsets, and ecl plane cut

% should eventually try re-making 2d scatterplot figure in python..

@@

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{Our best-fit $T_2$, binned to 27.5$'$ resolution}
\end{center}
\end{figure*}

>>>>

\subsection{Rectifying Reddening Residuals}
In this section we describe our attempts to eliminate the systematic
problems in the two-component reddening residuals shown in the left column
of Figure \ref{fig:resid}. We employed two main strategies: (1) recomputing
the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
the input maps and/or changing the particular two-component model adopted and
(2) making spatial cuts to isolate sky regions in which the 
residuals are especially pristine (or especially problematic).

The following is a list of dust model modifications we tested, but 
proved to have little impact on the reddening residual trends versus either 
$E(B-V)_{SFD}$ or $T_2$:

@@

However, we found that changing the zero level offsets of the input maps 
had a significant effect on the strength of the anticorrelation between median 
reddening residual and $T_2$. In particular, we experimented with perturbing 
the zero level offset of \PLANCK~857 GHz while correspondingly changing the 
zero levels of the remaining \PLANCK~maps based on the prescription of 
$\S$\ref{sec:relzero}. We also experimented with changing the zero level of SFD
\verb|i100|, independent of the other zero levels. Unfortunately, completely
flattening the reddening residual dependence on $T_2$ required unreasonably 
large zero level changes. For example, flattening the $T_2$ residual required
adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Such an offset is 
implausible, being an order of magnitude larger than the nominal \verb|i100| 
zero level uncertainty quoted by SFD98, and comparable to the entire 3000 GHz 
CIB monopole signal. Furthermore, we note that even these large zero 
level modifications had virtually no effect in eliminating the reddening 
residual `bend' versus $E(B-V)_{SFD}$. Thus, changing the zero level 
offsets showed hints of promise in rectifying the residual temperature 
dependence, but cannot completely resolve the systematic trends in reddening 
residuals.
% last few words here are kind of bad, need better terminology

The ony solution we were able to identify that both removed the `bend' vs.
$E(B-V)_{SFD}$ and the temperature dependence of the residual was cutting 
out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
completely eliminated the bending behavior of the residual versus 
$E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
\ref{fig:resid_ecl}), to a peak-to-peak amplitude of only $\sim$10 mmag. We
still included the single-MBB plots (right column), to show that 
the bend versus $E(B-V)_{SFD}$ is eliminated by the $|\beta|$ cut, even
for the single-MBB model. However, the single-MBB residuals still differ
systematically from zero for $T$$\lesssim$$19$ K. Perhaps these improvements in
the two-component reddening residuals after restricting to high ecliptic 
latitude should come as no surprise, given that the ecliptic plane is the most 
obvious systematic problem with the temperature correction upon inspecting the 
full-sky temperature map in Figure \ref{fig:results}.

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid_ecl.eps, width=6.6in}
\caption{\label{fig:resid_ecl} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$. The 
grayscale represents the conditional probability within each bin in SFD 
$E(B-V)$. The central black line shows the moving median. The upper and lower 
black lines represent the moving 75th and 25th percentiles respectively.}
\end{center}
\end{figure*}

@@

@@

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{\label{fig:results} Our best-fit $T_2$, binned to 27.5$'$ resolution}
\end{center}
\end{figure*}
